# Welcome {.unnumbered}

Welcome to my portfolio!I am Sohail, an aspiring Data Scientist and I'm passionate about understanding the flow of data from the bottom up, from data generation to AI/ML. I/m skilled at Python, SQL, ETl/ELT, Databricks, AWS/Azure, Statistical Machine Learning along with some experience in Data Engineering Fundamentals. Please, use the side bar on the left for navigation.


```{r}
#| output: false
#| echo: false

packages <- c("wordcloud2", "here")
```

```{r}
#| output: false
#| echo: false

install.packages(setdiff(packages, rownames(installed.packages())), repos = "http://cran.us.r-project.org")
```

```{r}
#| output: false
#| echo: false
#| message: false

lapply(packages, require, character.only = TRUE)
```

```{r}
#| output: false
#| echo: false

ds <- read.csv(here("data", "raw", "msg.csv"))
```

```{r}
# echo: false

# wordcloud2(data = ds, shape = "cardioid")
```

<div class="contact-footer">
[Email](mailto:smohamm2@macalester.edu){.btn-contact}
[GitHub](https://github.com/Sohail-44){.btn-contact}
[LinkedIn](https://www.linkedin.com/in/mohammed-sohail-khan-46489922a/){.btn-contact}
[Data Science Portfolio](https://mac-stat212-f25.github.io/portfolio-Sohail-44/){.btn-contact}
[Statistical ML Portfolio](https://sohail-44.github.io/StatsML/){.btn-contact}
</div>
